---
title: "The company referents keep: Learning multiple kinds of associations during cross-situational word learning"
output: html_document
---

**Zettersten, Wojcik, Benitez, & Saffran (2017)**

This is a walkthrough of the main analyses reported in the manuscript.

**Setting up the workspace and loading the data**

Load required R packages.

```{r, warning=FALSE, message=FALSE}
#load required R packages
source("summarizeData.R") #script for summarizing data, courtesy of "R cookbook" (http://www.cookbook-r.com/)
library(utils) #version 3.3.1
library(plyr) #version 1.8.4
library(ggplot2) #version 2.2.1
library(lme4) #version 1.1-14
library(stats) #version 3.3.1
library(cowplot) #version 0.8.0
library(AICcmodavg) #version 2.1-1
library(reshape2) #version 1.4.2
library(gtools) #version 3.5.0

```

Load in the full experimental dataset.

```{r}
d = read.table("CrossSit.txt",sep="\t", header=TRUE)
```


##Experiment 1

First, subset the data to the data for Experiment 1.

```{r}
exp1D = subset(d, expName=="exp1")
```

**Word Learning Model**

```{r}
#word learning model
mLearn_exp1=glmer(isRight~offset(logit(offset.25))+orderByTargetRoleC+(1+orderByTargetRoleC|ResponseID)+(1+orderByTargetRoleC|targetRole),data=subset(exp1D, trialKind=="training"),family=binomial, control=glmerControl(optimizer="bobyqa"))
summary(mLearn_exp1)
#compute Wald 95% CIs
confint(mLearn_exp1,method="Wald")[7:8,]
```

**Object Association Memory**

```{r}
# object-object association memory model
mMemory_exp1=glmer(isRight~offset(logit(offset.33))+(1|ResponseID)+(1|pairKind),data=subset(exp1D, trialKind=="test"),family=binomial,control=glmerControl(optimizer="bobyqa"))
summary(mMemory_exp1)
confint(mMemory_exp1,method="Wald")[3,]
```


**Analyze object-object memory vs. word learning tradeoff**

```{r}
mTradeoff_exp1=glmer(isRight~offset(logit(offset.25))+memAccExemplarTrialC+(1+memAccExemplarTrialC|ResponseID)+(1+memAccExemplarTrialC|targetRole), data=subset(exp1D,trialKind=="training"),family=binomial,control=glmerControl(optimizer="bobyqa"))
summary(mTradeoff_exp1)
confint(mTradeoff_exp1,method="Wald")[7:8,]
```

##Experiment 2

Subset the data to the data for Experiment 2.

```{r}
exp2D = subset(d, expName=="exp2")
```

**Word Learning Model**

```{r}
#Word Learning Model
mLearn_exp2=glmer(isRight~offset(logit(offset.25))+orderByTargetRoleC+(1+orderByTargetRoleC|ResponseID)+(1+orderByTargetRoleC|targetRole),data=subset(exp2D, trialKind=="training"),family=binomial, control=glmerControl(optimizer="bobyqa"))
summary(mLearn_exp2)
#compute Wald 95% CIs
confint(mLearn_exp2,method="Wald")[7:8,]
```

**Compare Word Learning Experiment 1 & 2**

``` {r}
#Compare Experiment 1 & 2
mLearn_exp12=glmer(isRight~offset(logit(offset.25))+distributionC*orderByTargetRoleC+(1+orderByTargetRoleC|ResponseID)+(1+orderByTargetRoleC:distributionC|targetRole),data=subset(d, trialKind=="training"&(expName=="exp1"|expName=="exp2")),family=binomial,control=glmerControl(optimizer="bobyqa"))
summary(mLearn_exp12)
confint(mLearn_exp12,method="Wald")[7:10,]
#note: the model including full by-item random effects structure did not converge, so we fit the model including only the random slope for the interaction, following Barr (2013)
```

**Object Association Memory Model**

```{r}
# object-object association memory model
mMemory_exp2=glmer(isRight~offset(logit(offset.33))+(1|ResponseID)+(1|pairKind),data=subset(exp2D, trialKind=="test"),family=binomial,control=glmerControl(optimizer="bobyqa"))
summary(mMemory_exp2)
confint(mMemory_exp2,method="Wald")[3,]
```

**Compare Experiment 1 and Experiment 2 Association Memory Accuracy**

```{r}
#Compare Experiment 1 & 2
mMemory_exp12=glmer(isRight~offset(logit(offset.33))+distributionC+(1|ResponseID)+(1+distributionC|pairKind),data=subset(d, trialKind=="test"&(expName=="exp1"|expName=="exp2")),family=binomial,control = glmerControl(optimizer="bobyqa"))
summary(mMemory_exp12)
confint(mMemory_exp12,method="Wald")[5:6,]
```

**Analyze object-object association memory vs. word learning tradeoff**

```{r}
mTradeoff_exp2=glmer(isRight~offset(logit(offset.25))+memAccExemplarTrialC+(1+memAccExemplarTrialC|ResponseID)+(1+memAccExemplarTrialC|targetRole), data=subset(exp2D,trialKind=="training"),family=binomial,control=glmerControl(optimizer="bobyqa"))
summary(mTradeoff_exp2)
confint(mTradeoff_exp2,method="Wald")[7:8,]
```

**Compare Tradeoffs for Experiment 1 and Experiment 2**

```{r}
mTradeoff_exp12=glmer(isRight~offset(logit(offset.25))+distributionC*memAccExemplarTrialC+(1+memAccExemplarTrialC|ResponseID)+(1+memAccExemplarTrialC:distributionC|targetRole), data=subset(d, trialKind=="training"&(expName=="exp1"|expName=="exp2")),family=binomial,control=glmerControl(optimizer="bobyqa"))
summary(mTradeoff_exp12)
confint(mTradeoff_exp12,method="Wald")[7:10,]
#note: the model including full by-item random effects structure did not converge, so we fit the model including only the random slope for the interaction, following Barr (2013)
```

##Experiment 3

Subset the data to the data for Experiment 3.

```{r}
exp3D = subset(d, expName=="exp3_uniform"|expName=="exp3_skewed")
```

**Word Learning Model**

```{r}
#Word Learning Model
mLearn_exp3=glmer(isRight~offset(logit(offset.25))+distributionC*orderByTargetRoleC+(1+orderByTargetRoleC|ResponseID)+(1+orderByTargetRoleC:distributionC|targetRole),data=subset(exp3D, trialKind=="training"),family=binomial, control=glmerControl(optimizer="bobyqa"))
summary(mLearn_exp3)
#compute Wald 95% CIs
confint(mLearn_exp3,method="Wald")[7:10,]
#note: the model including full by-item random effects structure did not converge, so we fit the model including only the random slope for the interaction, following Barr (2013)
```

**Object-Object Association memory model**

```{r}
# object-object association memory model
mMemory_exp3=glmer(isRight~offset(logit(offset.33))+distributionC+(1|ResponseID)+(1+distributionC|pairKind),data=subset(exp3D, trialKind=="test"),family=binomial,control=glmerControl(optimizer="bobyqa"))
summary(mMemory_exp3)
confint(mMemory_exp3,method="Wald")[5:6,]

#recode to test skewed condition against chance
exp3D$distributionSkewed = varRecode(exp3D$distributionC,c(-0.5,0.5),c(-1,0))
mMemory_exp3Skewed=glmer(isRight~offset(logit(offset.33))+distributionSkewed+(1|ResponseID)+(1+distributionSkewed|pairKind),data=subset(exp3D, trialKind=="test"),family=binomial,control=glmerControl(optimizer="bobyqa"))
summary(mMemory_exp3Skewed)
confint(mMemory_exp3Skewed,method="Wald")[5:6,]

#recode to test uniform condition against chance
exp3D$distributionUniform = varRecode(exp3D$distributionC,c(-0.5,0.5),c(0,1))
mMemory_exp3Uniform=glmer(isRight~offset(logit(offset.33))+distributionUniform+(1|ResponseID)+(1+distributionUniform|pairKind),data=subset(exp3D, trialKind=="test"),family=binomial,control=glmerControl(optimizer="bobyqa"))
summary(mMemory_exp3Uniform)
confint(mMemory_exp3Uniform,method="Wald")[5:6,]
```


**Analyze object-object memory vs. word learning tradeoff**

```{r}
##analyze object-object memory vs. word learning tradeoff##
mTradeoff_exp3=glmer(isRight~offset(logit(offset.25))+distributionC*memAccExemplarTrialC+(1+memAccExemplarTrialC|ResponseID)+(1+distributionC*memAccExemplarTrialC|targetRole), data=subset(exp3D,trialKind=="training"),family=binomial,control=glmerControl(optimizer="bobyqa"))
summary(mTradeoff_exp3)
confint(mTradeoff_exp3,method="Wald")[14:17,]
```
